---
title: "RFCDE"
author: "Taylor Pospisil"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RFCDE}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
devtools::load_all()
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library("ggplot2")
```

Random forests is a common non-parametric regression technique which
performs well for mixed-type data and irrelevant covariates, while
being robust to monotonic variable transformations. RFCDE fits random
forest models optimized for nonparametric conditional density
estimation.

## Example
```{r load_functions, echo = F, message = F, eval = F}
devtools::load_all()
```


```{r set parameters}
m <- 1e4
nfolds <- 3
nfolds <- 5
nbins <- 5
node_size <- floor(m / (3 * nbins)) # todo smaller trees are ok for forest
```

```{r}

folds <- sample(1:nfolds, m, replace = TRUE)

cov1 <- runif(m, -1, 1)
cov2 <- runif(m, -1, 1)
prop_alt <- 1 / (1 + exp(-1 * (3 * cov1 + 2 * cov2 - 5)))
Ps <- ifelse(rbinom(m, size = 1, prop_alt),
  rbeta(m, 0.25, 1),
  runif(m)
)
noise_dim <- 1
covariate <- cbind(cov1, cov2)
noise <- matrix(rnorm(noise_dim*m), m)
#Xs <- cbind(covariate,noise)
Xs <- covariate
```

### Training

Trees are recursively partitioned to minimize the CDE loss

$$ \int \int (\hat{f}(x \mid z) - f(x \mid z))^{2} dz dP(x) $$

This is efficiently calculated using an orthogonal series
representation of the conditional densities. The resolution of this
representation is controlled by `n_basis`.


### Prediction

We use the forest structure to determine weights for a weighted kernel
density estimate. The `predict` function evaluates this density on the
provided grid.

#group_by_forest2 <- function(pvalues, covariates, folds, nfolds, nbins, ntrees = 10, seed=NULL)

```{r}
n_trees <- 1
mtry <- 4
n_basis <- 10
groups <- matrix(0, nrow = nrow(Xs), ncol = n_trees)

i <- 1
for (i in seq_len(nfolds)) {
  # Ps_holdout_fold <- Ps[folds == i]
  # Xs_holdout_fold <- Xs[folds == i, ]
  holdout_fold <- which(folds != i)
  Ps_other_folds <- Ps[folds != i]
  Xs_other_folds <- Xs[folds != i, ]

  forest_other_folds <- RFCDE(
    x_train = Ps_other_folds, z_train = Xs_other_folds, n_trees = n_trees, mtry = mtry,
    node_size = node_size, n_basis = n_basis, basis_system = "cosine"
  )

  forest_other_folds$rcpp$set_leaves_id()

  for (j in holdout_fold) {
    groups[j, ] <- forest_other_folds$rcpp$traverse_forest(Xs[j, ]) #TODO as matrix
  }
}

groups <- as.data.frame(groups)
groups[] <- lapply(groups, as.factor)
colnames(groups) <- paste0("group", seq_along(groups))
```

```{r}
df <- data.frame(
  Xs = Xs,
  groups = groups,
  folds = folds
)
class(df)
names(df)
df %>% 
  #filter(folds == 1) %>% 
  ggplot(aes(Xs.cov1, Xs.cov2, color = group1)) +
  geom_point()
```
